Intro Seminar

### 2017-03-23 doc/seminar2017.Rmd
Assessed vitamin D and inflammation (CRP)

>>>>

## Inflammation

```{r CRP}

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  scatter_plot("log(CRP)", "VitaminD",
               "CRP", "25(OH)D")

  mason::design("glm") %>% 
  mason::add_settings(family = stats::gaussian()) %>% 
  mason::add_variables("yvars", "VitaminD") %>% 
  mason::add_variables("xvars", "CRP") %>% 
  mason::construct() %>% 
  mason::scrub()
```

## Hyperfiltration
